Shedding Light on the ``Dark Side'' of Phylogenetic Comparative Methods

### 2015-12-23 Manuscript/dark.tex
Final edits prepublication

  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=12cm]{Figures/PCMCitations.pdf}
      \caption{The number of papers containing the phrase ``phylogenetic comparative'' published each year from 1980-2014 (Google Scholar search April 13th 2015).}
      \label{PCMCitations}
  \end{figure}

\newpage
  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=12cm]{Figures/PCMRpackages.pdf}
      \caption{The cumulative total number of R packages for phylogenetics and phylogenetic comparative methods through time from 1980-2014. Source: Brian O'Meara's ``CRAN Task View: Phylogenetics, Especially Comparative Methods'' version 2015-01-21.}
      \label{PCMRpackages}
  \end{figure}

>>>>

  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=12cm]{Figures/PCMCitations.pdf}
      \caption{The number of papers containing the phrase ``phylogenetic comparative'' published each year from 1980-2014 (Google Scholar search April 13th 2015). Data are available from figshare \citep{coopermeedata}.
}
      \label{PCMCitations}
  \end{figure}

\newpage
  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=12cm]{Figures/PCMRpackages.pdf}
      \caption{The cumulative total number of R packages for phylogenetics and phylogenetic comparative methods through time from 1980-2014. Source: Brian O'Meara's ``CRAN Task View: Phylogenetics, Especially Comparative Methods'' version 2015-01-21. Data are available from figshare \citep{coopermeedata}.
}
      \label{PCMRpackages}
  \end{figure}
